### 2016-09-06 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the answers and minor text cleanings in the note

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g. 1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).\\
   \textcolor{blue}{The reconstructed incoherent asymmetries are presented in 
      figure \ref{fig:BSA_incoherent_epMM} with the associated exlcusive 
      distributions in figure \ref{fig:epMM2_incoh_exc_cuts}. The different 
   tail cuts show no major effects on the reconstructed ALU.}

@@

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.
  \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.png}
    \caption{ Fitting e1dvcs1 free proton beam-spin asymmetries. The dashed 
    curves are fits to the data in the form of 
 $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$, while the solid curves are from 
 calculations based on fitting the parameters $p_{0}$ and $p_{1}$.}
    \label{fig:free-proton-alu-fits}
    \end{figure}

@@

Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm].
Otherwise, even if you do not show it in the CAN, mention in one line that a 
specific study was done.
\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.\\
    \textcolor{blue}{We implemented a 4D ratio R for the background 
       subtraction. The difference between the reconstructed ALU with 2D and 4D 
       background subtraction are presented in figures \ref{fig:coh_binning} 
       and \ref{fig:incoh_binning} for the coherent and the incoherent DVCS 
       channels. Even though the 2D was a good a pproximation, a 4D subtraction 
    is applied on the final results.} 
    \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_Coherent_xB.png}
    \includegraphics[height=6.6cm]{fig/diff_BSA_Coherent_xB.png}
    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
    function of $\phi$ in $x_{B}$ bins using 2D (in blue) and 4D (in green) 
 background subtraction.  On bottom: the difference between the two asymmetries 
 as a function of $\phi$.}
    \label{fig:coh_binning}
    \end{figure}

@@

\item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again.

@@

\item Please keep a record of the changes in the CAN, as we will probably not 
re-read the whole text.

\item Request to see the very first draft of the publication.

>>>>

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g. 1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).\\
   \textcolor{blue}{The reconstructed incoherent asymmetries are presented in 
   figure \ref{fig:BSA_incoherent_epMM} with the associated exclusive 
distributions in figure \ref{fig:epMM2_incoh_exc_cuts}. We conclude that the 
different tail cuts show no major effects on the reconstructed $A_{LU}$.}

@@

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.\\
  \textcolor{blue}{We changed the procedures completely, see Appendix G in the 
  latest version of the analysis note. We performed fittings for the published 
  free proton asymmetries. Then we used those fits to extrapolate the free 
  proton asymmetries at our measured kinematics}.\\
  \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.png}
    \caption{ Fitting e1dvcs1 free proton beam-spin asymmetries. The dashed 
    curves are fits to the data in the form of 
 $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$, while the solid curves are from 
 calculations based on fitting the parameters $p_{0}$ and $p_{1}$.}
    \label{fig:free-proton-alu-fits}
    \end{figure}

@@

Figs 1-4 of 
\url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm]. Otherwise, even if you do not show it in the 
CAN, mention in one line that a specific study was done.\\
\textcolor{blue}{The analysis note has been updated with all the required 
plots. See Q.7 for the new updates in the note.}\\

\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.\\
    \textcolor{blue}{We implemented a 4D ratio R for the background 
       subtraction. The difference between the reconstructed ALU with 2D and 4D 
       background subtraction are presented in figures \ref{fig:coh_binning} 
       and \ref{fig:incoh_binning} for the coherent and the incoherent DVCS 
    channels. Even though the 2D was a good approximation, a 4D subtraction is 
 applied on the final results.}

 \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_Coherent_xB.png}
    \includegraphics[height=6.6cm]{fig/diff_BSA_Coherent_xB.png}
    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
    function of $\phi$ in $x_{B}$ bins using 2D (in blue) and 4D (in green) 
 background subtraction.  On bottom: the difference between the two asymmetries 
 as a function of $\phi$.}
    \label{fig:coh_binning}
    \end{figure}

@@

\item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again. \\
   \textcolor{blue}{Sorry there was a missig sign. This is the correct 
      dependence.
      \begin{equation}
       \frac{\partial MM^2_{e\gamma X}}{\partial E_{\gamma}}
                     = -2*(E_{\gamma^{*}} + M_{target} - E_{\gamma})
                      \label{eq:egamma}
                      \end{equation}
        }

@@

\item Please keep a record of the changes in the CAN, as we will probably not 
   re-read the whole text.\\
\textcolor{blue}{\begin{enumerate}
      \item Added the run conditions section 1.2.4.
      \item Updated figure 2.2.
      \item Update section 2.1.3 Track reconstruction.
      \item Update section 2.2.1.1
      \item Added section 2.2.1.3 Checking the initial good track requirements.
      \item Cleaning section 2.2.2 with adding a summary for the drift paths 
         and the drift speed calibrations, section 2.2.2.3
      \item Cleaning section 2.2.3 Gain calibration with adding more demanded 
         plots.
      \item Added section 2.4 RTPC efficiency.
      \item Cleaned section 3.2.5 with adding the required plots.
      \item Added the demanded plots in section 4.1.2 and cleaning the writing.
      \item Added a new section 4.1.3 regarding checking the selected coherent 
         DVCS events.
      \item Edited the plots in figure 4.15 with the -tmin lines.
      \item Cleaning section 4.5 after changing to perform 4D background 
         subtraction with a summery about other background sources and a new 
         section for the accidental contaminations.
      \item Updated section 4.7 Systematic uncertainties with all suggested 
         studies.
      \item Updated section 5.1 with the new fitting procedures for the 
         coherent channel.
      \item Updated all the figure in chapter 5 with the new results and the 
         suggested modifications.
      \item Added Appendix F with $A_{LU}$ tables.
      \item Added Appendix G for the free proton asymmetry interpolations.
   \end{enumerate} }

\item Request to see the very first draft of the publication.
    \textcolor{blue}{Will be provided}.
